Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-12 files/Chapter1/2DModel.tex
symbols
table of symbols

Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$\textcolor{red}{;} $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$. Then using the definition of strain 
\begin{eqnarray}
	\partial_i u_3 = 0 \quad \textrm{ for } i = 1,2,3 \textrm{ on } \Omega.
\end{eqnarray}

It follows that $u_3$ is a constant on $\Omega$ and $u$ is a vector valued function in $R_2$ with two-dimensional stress and strain. The out of plane conditions for strain \eqref{plane_stress_neseccary_condition} falls away and Hooke’s law can be written in a two-dimensional form using the stress components (1.2.16) as $\displaystyle T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E})I.$\\

\subsection{Equations of motion and constitutive equations}\label{ssec:2D_Model:EquationsOfMotion+ConstitutiveEquations}
 The following equations of motion and constitutive equations follow from subsections \ref{ssec:3D_Model:DimensionlessForm} and 1.3.2.
\subsubsection{Equation of motion}\label{sssec:2D_Model:EquationOfMotion}
\begin{eqnarray}
	\partial_t^2 u & = & \textrm{div}T + Q, \label{eq:2D_Model:EM}
\end{eqnarray}
where
\begin{eqnarray}
	\textrm{div} T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22}
	\end{bmatrix}. \label{eq:2D_Model:DivT}
\end{eqnarray}
\subsubsection{Constitutive equation}\label{sssec:2D_Model:ConstitutiveEquation}
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E}) I. \label{eq:2D_Model:CE}
\end{eqnarray}

\subsection{Model problem}\label{ssec:2D_Model:ModelProblem}
Suppose $\Omega \subset R_2$ is the reference configuration for a solid executing small vibrations. The boundary of $\Omega$ consists of two parts $\Sigma$ and $\Gamma$. The model problem is described as:
\begin{itemize}
    \item[] The equation of motion \eqref{eq:2D_Model:EM} and constitutive equation \eqref{eq:2D_Model:CE} are satisfied in $\Omega$.
	\item[] The displacement $u$ is specified on $\Sigma$;
	\item[] Traction $Tn$ is specified on $\Gamma$.
\end{itemize}

@@

Instead of volume integrals ($dV$) and surface integrals ($dS$), the two-dimensional model has area ($dA$) and line integrals ($ds$). Rather than the divergence formula, the divergence form of Green's formula is used to obtain the following result:
\begin{eqnarray*}
	\int_{\Omega} \textrm{div}(T)\cdot \phi \ dA & = & -\int_{\Omega} \textrm{Tr}(T\Phi) \ dA + \int_{\Gamma} Tn\cdot \phi ds.
\end{eqnarray*}

@@

\subsubsection{Test functions for problem 2D-1}\label{sssec:2D_Model:TestFunctions2D1}
The test function space has the same definition of the test function space for Problem 3D-1. But since $\Omega \in R_2$, we have that $T(\Omega) \subset R_2$.
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
\end{eqnarray*}

>>>>

Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$; $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$. Then using the definition of strain 
\begin{eqnarray}
	\partial_i u_3 = 0 \quad \textrm{ for } i = 1,2,3 \textrm{ on } \Omega.
\end{eqnarray}

It follows that $u_3$ is a constant on $\Omega$ and $u$ is a vector valued function in $R^2$ with two-dimensional stress and strain. The out of plane conditions for strain \eqref{plane_stress_neseccary_condition} falls away and Hooke’s law can be written in a two-dimensional form using the stress components (1.2.16) as $\displaystyle T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E})I.$\\

\subsection{Equations of motion and constitutive equations}\label{ssec:2D_Model:EquationsOfMotion+ConstitutiveEquations}
 The following equations of motion and constitutive equations follow from subsections \ref{ssec:3D_Model:DimensionlessForm} and 1.3.2.
\subsubsection{Equation of motion}\label{sssec:2D_Model:EquationOfMotion}
\begin{eqnarray}
	\partial_t^2 u & = & \textrm{div}T + Q, \label{eq:2D_Model:EM}
\end{eqnarray}
where
\begin{eqnarray}
	\textrm{div} T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22}
	\end{bmatrix}. \label{eq:2D_Model:DivT}
\end{eqnarray}
\subsubsection{Constitutive equation}\label{sssec:2D_Model:ConstitutiveEquation}
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{Tr}(\mathcal{E}) I. \label{eq:2D_Model:CE}
\end{eqnarray}

\subsection{Model problem}\label{ssec:2D_Model:ModelProblem}
Suppose $\Omega \subset R^2$ is the reference configuration for a solid executing small vibrations. The boundary of $\Omega$ consists of two parts $\Sigma$ and $\Gamma$. The model problem is described as:
\begin{itemize}
    \item[] The equation of motion \eqref{eq:2D_Model:EM} and constitutive equation \eqref{eq:2D_Model:CE} are satisfied in $\Omega$.
	\item[] The displacement $u$ is specified on $\Sigma$;
	\item[] Traction $Tn$ is specified on $\Gamma$.
\end{itemize}

@@

Instead of volume integrals ($dV$) and surface integrals ($dS$), the two-dimensional model has area ($dA$) and line integrals ($ds$). Rather than the divergence formula, the divergence form of Green's formula is used to obtain the following result:\label{sym:dV}\label{sym:dS}\label{sym:dA}\label{sym:ds}
\begin{eqnarray*}
	\int_{\Omega} \textrm{div}(T)\cdot \phi \ dA & = & -\int_{\Omega} \textrm{Tr}(T\Phi) \ dA + \int_{\Gamma} Tn\cdot \phi ds.
\end{eqnarray*}

@@

\subsubsection{Test functions for problem 2D-1}\label{sssec:2D_Model:TestFunctions2D1}
The test function space has the same definition of the test function space for Problem 3D-1. But since $\Omega \in R^2$, we have that $T(\Omega) \subset R^2$.
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}. 
\end{eqnarray*}\label{sym:baromega}

### 2023-11-12 files/Chapter1/3DModel.tex
table of symbols

\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
Suppose $\Omega \subset R_3$ is the reference configuration for a solid
executing small vibrations. The boundary of $\Omega$ can be divided into two
distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be
considered a model problem for a three-dimensional elastic body.
\begin{enumerate}
	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
	\item[] The displacement $u = u_\Sigma$ is specified on
		$\Sigma$;
	\item[] The traction $Tn = t_\Gamma$ is specified on
		$\Gamma$.
\end{enumerate} \label{sym:n}\label{sym:SigmaGamma}

@@

Boundary Conditions:
\begin{eqnarray*}
	Tn & = & 0 \quad \textrm{ on } \partial\Omega
\end{eqnarray*} With $n$ the unit outward normal vector.

@@

Consider the right-hand orthonormal set $\left\{e_1, e_2, e_3\right\}$. Without
loss of generality, assume the stresses act parallel to the $e_1$-$e_2$ plane
i.e. $\sigma_{3i} = 0$ for all $i$. From Hooke's Law \eqref{DM_H_E} the
following equations are obtained:

>>>>

\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
Suppose $\Omega \subset R^3$ is the reference configuration for a solid
executing small vibrations. The boundary of $\Omega$ can be divided into two
distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be
considered a model problem for a three-dimensional elastic body.
\begin{enumerate}
	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
	\item[] The displacement $u = u_\Sigma$ is specified on
		$\Sigma$;
	\item[] The traction $Tn = t_\Gamma$ is specified on
		$\Gamma$.
\end{enumerate} \label{sym:n}\label{sym:SigmaGamma}

@@

Boundary Conditions:
\begin{eqnarray*}
	Tn & = & 0 \quad \textrm{ on } \partial\Omega
\end{eqnarray*} With $n$ the unit outward normal vector. \label{sym:boundaryOmega}

@@

Consider the right-hand orthonormal set $\left\{e_1, e_2, e_3\right\}$. Without
loss of generality, assume the stresses act parallel to the $e_1$-$e_2$ plane
i.e. $\sigma_{3i} = 0$ for all $i$. From Hooke's Law \eqref{DM_H_E} the
following equations are obtained: \label{sym:e_i}

### 2023-11-12 files/Chapter1/PlateModel.tex
table of symbols

\documentclass[../../main.tex]{subfiles}
\begin{document}
	\section{Reissner-Mindlin Plate Model} \label{sec:P_Model}
	Consider small vibrations of a plate. This motion can be described by using spherical coordinates. Assume that the plate has a two dimensional domain $\Omega \subset R_2$. For $r \geq 0$, the coordinates $x_1$ and $x_2$ can be rewritten as
	\[ x_1 = r \sin \phi \cos \theta, \]
	\[ x_2 = r \sin \phi \sin \theta. \]

@@

	\subsection{Equations of Motion and Constitutive Equations}\label{ssec:P_Model:EquationsOfMotion+ConstitutiveEquation}
	Consider a Reissner-Mindlin plate with reference configuration $\Omega \in R_2$. Let $u \in \Omega$ define the transverse motion of the plate model and $\psi = \langle \psi_1 \ \psi_2 \rangle$ the angle between the material line and a line perpendicular to the plate.

@@

	\subsection{Model Problems}\label{ssec:P_Model:ModelProblems}
	Let $\Omega \subset R_2$ denote reference configuration of the plate model. Following \cite{Wu05}, $\Omega$ is a rectangle.\\

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
	\section{Reissner-Mindlin Plate Model} \label{sec:P_Model}
	Consider small vibrations of a plate. This motion can be described by using spherical coordinates. Assume that the plate has a two dimensional domain $\Omega \subset R^2$. For $r \geq 0$, the coordinates $x_1$ and $x_2$ can be rewritten as
	\[ x_1 = r \sin \phi \cos \theta, \]
	\[ x_2 = r \sin \phi \sin \theta. \]

@@

	\subsection{Equations of Motion and Constitutive Equations}\label{ssec:P_Model:EquationsOfMotion+ConstitutiveEquation}
	Consider a Reissner-Mindlin plate with reference configuration $\Omega \in R^2$. Let $u \in \Omega$ define the transverse motion of the plate model and $\psi = \langle \psi_1 \ \psi_2 \rangle$ the angle between the material line and a line perpendicular to the plate.

@@

	\subsection{Model Problems}\label{ssec:P_Model:ModelProblems}
	Let $\Omega \subset R^2$ denote reference configuration of the plate model. Following \cite{Wu05}, $\Omega$ is a rectangle.\\

### 2023-11-12 files/Chapter2/generalvibrationmodel.tex
symbols
table of symbols

\subsection{The variational approach}\label{ssec:existence:VariationlApproach}
Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
\begin{itemize}
	\item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
	\item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
\end{itemize} \label{sym:Xspace}\label{sym:Wspace}\label{sym:Vspace}\label{sym:norm}

@@

\newtheorem{Thm3n}[Thmx]{Theorem}
\begin{Thm3n}[Strong Damping]
	If $a$ is positive definite on $V$, there exists a unique solution $u \in C^1([0,\infty),V)\cap C^2((0,\infty),W)$ for Problem GVar for any $u_0 \in V$, $u_1 \in W$ and any $f$ which is Lipschitz on $V$. If $f=0$, then $u \in C^1([0,\infty),V)\cap C^2([0,\infty),W)\cap C^\infty((0,\infty),V)$.
\end{Thm3n} \label{Cinfty}

@@

To determine if such a number $\lambda$ exists, consider the following eigenvalue problem.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

@@

\subsubsection*{Problem T-1EV}\label{sssec:1D_Model:ProblemT1EV}
Find a pair of functions $\tilde{w}$ and $\tilde{\phi}$ such that for all $t >0$, $\langle \tilde{w}\ \tilde{\phi}\rangle \in  T[0,1]$ and satisfying the equations
\begin{eqnarray*}
	 -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v' &=& \int_0^1 \lambda \tilde{w} v ,\\
	 -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi' &=& \int_0^1 \lambda \tilde{\phi} \psi .
\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$.

@@

In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by
\begin{eqnarray}
	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
\end{eqnarray}

@@

These comparisons are made in Chapter 4 and 6. Being able to express the solutions as a valid series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models. This is explained in detail in \cite{CVV18}.

In \cite{CVV18}, the authors consider a beam model and wave equation model for a vibrating string. Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solution. A comparison of the exact solutions are not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.

@@

\begin{proof}
	Suppose $f,g \in \mathbb{R}[a,b]$. Then
	\begin{eqnarray}
		\left| \int_a^b fg \right| & \leq & ||f||\ ||g|| \ \ \ \ \textrm{ by Cauchy-Swartz Inequality.} \label{CSI}
	\end{eqnarray}

>>>>

\subsection{The variational approach}\label{ssec:existence:VariationlApproach}
Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
\begin{itemize}
	\item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
	\item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
\end{itemize} \label{sym:Xspace}\label{sym:Wspace}\label{sym:Vspace}\label{sym:norm} \label{sym:innerproduct}

@@

\newtheorem{Thm3n}[Thmx]{Theorem}
\begin{Thm3n}[Strong Damping]
	If $a$ is positive definite on $V$, there exists a unique solution $u \in C^1([0,\infty),V)\cap C^2((0,\infty),W)$ for Problem GVar for any $u_0 \in V$, $u_1 \in W$ and any $f$ which is Lipschitz on $V$. If $f=0$, then $u \in C^1([0,\infty),V)\cap C^2([0,\infty),W)\cap C^\infty((0,\infty),V)$.
\end{Thm3n} \label{sym:Cinfty}

@@

To determine if such a number $\lambda$ exists, consider the following eigenvalue problem.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in R$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

@@

\subsubsection*{Problem T-1EV}\label{sssec:1D_Model:ProblemT1EV}
Find a pair of functions $\tilde{w}$ and $\tilde{\phi}$ such that for all $t >0$, $\langle \tilde{w}\ \tilde{\phi}\rangle \in  T[0,1]$ and satisfying the equations
\begin{eqnarray*}
	 -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v' &=& \int_0^1 \lambda \tilde{w} v ,\\
	 -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi' &=& \int_0^1 \lambda \tilde{\phi} \psi .
\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$. \label{sym:lambda}

@@

In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by \label{sym:Energy}
\begin{eqnarray}
	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
\end{eqnarray}

@@

These comparisons are made in Chapter 4 and 6. Being able to express the solutions as valid series solutions, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models. This is explained in detail in \cite{CVV18}.

In \cite{CVV18}, the authors consider a beam model and wave equation model for a vibrating string. Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solutions. A comparison of the exact solutions are not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.

@@

\begin{proof}
	Suppose $f,g \in R[a,b]$. Then
	\begin{eqnarray}
		\left| \int_a^b fg \right| & \leq & ||f||\ ||g|| \ \ \ \ \textrm{ by Cauchy-Swartz Inequality.} \label{CSI}
	\end{eqnarray}

### 2023-11-12 files/Chapter3/dynamicconvergence.tex
table of symbols

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
In this chapter, two important convergence results of the Finite Element Method
(FEM) is discussed. The first result looks at the convergence of the Galerkin
approximation for second order hyperbolic type problems, as presented
in~\cite{BV13}. The second result, from the textbook~\cite{SF97}, examines the
convergence of eigenvalues and eigenfunctions for a one-dimensional vibration
problem, using the Finite Element Method.

@@

Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary
differential equations denoted by Problem ODE. \subsubsection*{Problem ODE}
Find a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\bar{u}'' + C \bar{u}' + K\bar{u} = F(t) \ \ \ \textrm{ with } \bar{u}(0) = \bar{u}^h_0 \textrm{ and }  \bar{u}(1) = \bar{u}^h_1 \label{ODE}
\end{eqnarray}
The function $F$ is the interpolation of the function $f$ into the discrete space $S^h$.

@@

In \eqref{error_e}, the the error for the semi-discrete problem is the term $[u(t_k)-u_h(t_k)]$ and the term $[u_h(t_k) - u^h_k]$ is the error for the fully disrete appreximation of the semi-discrete approximation.

\subsection{Main result}

@@

\subsection{Fully discrete Galerkin finite element approximation}
\textcolor{red}{********************HOU VOORLOPIG**********************}
Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length
$\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for
$k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \
			t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$.\\

@@

From Theorem 2 of the semi-discrete problem an error estimate for
$[u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors
of \cite{BV13} then proceed to obtain an error estimate for $[u_h(t_k) -
			u^h_k]$. Since the dimension of $S^h$ is not fixed, the equivalence of norms
cannot be used, and therefore this error estimate for $[u_h(t_k) - u^h_k]$
should also be with respect to the norm of $W$.
\textcolor{red}{********************HOU VOORLOPIG**********************}

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\textcolor{red}{1973 is die original, en 1997 is 'n update tot die 1973 met extra voorbeelde, kode en oefeninge. Die 1997 is die die kopie wat ek het. So prof moet se as ek 1973 eerder moet gebruik.}

In this chapter, two important convergence results of the Finite Element Method
(FEM) is discussed. The first result looks at the convergence of the Galerkin
approximation for second order hyperbolic type problems, as presented
in~\cite{BV13}. The second result, from the textbook~\cite{SF97}, examines the
convergence of eigenvalues and eigenfunctions for a one-dimensional vibration
problem, using the Finite Element Method.

@@

Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary
differential equations denoted by Problem ODE. \subsubsection*{Problem ODE}
Find a function $\bar{u} \in S^h$ such that \label{sym:baru}
\begin{eqnarray}
	M\bar{u}'' + C \bar{u}' + K\bar{u} = F(t) \ \ \ \textrm{ with } \bar{u}(0) = \bar{u}^h_0 \textrm{ and }  \bar{u}(1) = \bar{u}^h_1 \label{ODE}
\end{eqnarray}
The function $F$ is the interpolation of the function $f$ into the discrete space $S^h$.

@@

In \eqref{error_e}, the the error for the semi-discrete problem is the term $u(t_k)-u_h(t_k)$ and the term $u_h(t_k) - u^h_k$ is the error for the fully disrete appreximation of the semi-discrete approximation.

\subsection{Main result}
\textcolor{red}{************** NIE DIE MAIN RESULT NIE*******************}

@@

\subsection{Fully discrete Galerkin finite element approximation}
\textcolor{red}{********************HOU VOORLOPIG**********************}

Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length
$\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for
$k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \
			t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$.\\

@@

From Theorem 2 of the semi-discrete problem an error estimate for
$[u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors
of \cite{BV13} then proceed to obtain an error estimate for $[u_h(t_k) -
			u^h_k]$. Since the dimension of $S^h$ is not fixed, the equivalence of norms
cannot be used, and therefore this error estimate for $[u_h(t_k) - u^h_k]$
should also be with respect to the norm of $W$.

\textcolor{red}{********************HOU VOORLOPIG**********************}

\textcolor{red}{Dupliseering maar moontlik beter as werk net voor Main Result, p52}

### 2023-11-12 files/Chapter4/CantileverTimo.tex
table of symbols

\subsubsection{Problem Var} Find the functions $w$, $\phi$, $V$ and $\theta$ such that $\langle w(\cdot,t), \phi(\cdot,t) \rangle \in T[0,1] \times C^1[0,1]$, $V(\cdot,t) \in C^1[0,1]$ and $\theta(t) \in \mathbb{R}$ for all $t>0$ and the following equations hold:
\begin{align}
\int_0^1 \partial^2_t w(\cdot,t) f \ dx  & =   \int_0^1~ V(\cdot,t) f' \ dx - c_1\int_0^1 \partial_t w(\cdot,t)f \ dx + \int_0^1q(\cdot,t)f \ dx \nonumber \\
 &  -(m \partial_t^2 w(1,t) +  md \ddot \theta(t) + k_1 \partial_t w(1,t) + k_1 d \dot \theta(t))f(1), \label{CT_18}\\
\int_0^1 \frac{1}{\alpha}~\partial^2_t \phi(\cdot,t) g \ dx  &= -\int_0^1\dfrac{1}{\beta} \partial_x \phi(\cdot,t)g' \ dx - c_2 \int_0^1 \partial_t \partial_x \phi(\cdot,t)g' \ dx + \int_0^1 V(\cdot,t)g \ dx \nonumber \\
 &  +\gamma \big(\theta(t) - \phi(1,t)\big)g(1) - \mu \phi(0,t)g(0), \label{CT_19}\\
\int_0^1 V(\cdot,t)h \ dx &= \int_0^1 \partial_x w(\cdot,t)h \ dx - \int_0^1 \phi(\cdot,t)h \ dx,  \label{CT_20}
\end{align}
with the interface equation,
\begin{align}
(J+ md^2) \ddot \theta(t)+ (k_1d^2 + d k_2) \dot \theta(t)  + dm \partial_t^2 w(1,t)
  + dk_1 \partial_t w(1,t) \nonumber\\
  =  -\gamma \big(\theta(t) - \phi(1,t)\big),  \label{CT_21}
\end{align}

@@

\subsection{Galerkin approximation}
Create a set of n+1 linear basis functions $\delta_i$, where $\delta_i \in C[0,1]$ for $i = 0,1,2,...,n$. Let $S_0 = \textrm{span}\left\{\delta_0,\delta_1,\delta_2,...,\delta_n\right\}$ and $S = \textrm{span}\left\{\delta_1,\delta_2,\delta_3,...,\delta_n\right\}$.

\subsubsection{Problem G}
Find the functions $w^h$, $\phi^h$, $V^h$ and $\theta^h$ such that $w^h(\cdot,t) \in S$,  $\phi^h(\cdot,t),V^h(\cdot,t) \in S_0$ and $\theta^h(t) \in \mathbb{R}$ for all $t>0$ and the following equations hold:

@@

\subsubsection{Problem ODE}
Find the functions $\bar{w} \in S$, $\bar{\phi}, \bar{V} \in S_0$ and $\theta^h \in \mathbb{R}$ such that
\begin{align}
M_w\ddot{\bar{w}} = L_w\bar{V} -\big(m \ddot{w}_{n+1}(t) + k_1 \dot{w}_{n+1}(t) \big)\delta_i(1) + M^* \bar{q}(t) + \bar{q}_I,\\
\label{sys2}
\frac{1}{\alpha} M \ddot{\bar{\phi}} = -\frac{1}{\beta} K\bar{\phi} + M\bar{V} + \tilde{G},\\
\label{sys2.1}
\bar{0} = -M\bar{V} + L^T\bar{w} - M\bar{V}.
\end{align}

>>>>

\subsubsection{Problem Var} Find the functions $w$, $\phi$, $V$ and $\theta$ such that $\langle w(\cdot,t), \phi(\cdot,t) \rangle \in T[0,1] \times C^1[0,1]$, $V(\cdot,t) \in C^1[0,1]$ and $\theta(t) \in R$ for all $t>0$ and the following equations hold:
\begin{align}
\int_0^1 \partial^2_t w(\cdot,t) f \ dx  & =   \int_0^1~ V(\cdot,t) f' \ dx - c_1\int_0^1 \partial_t w(\cdot,t)f \ dx + \int_0^1q(\cdot,t)f \ dx \nonumber \\
 &  -(m \partial_t^2 w(1,t) +  md \ddot \theta(t) + k_1 \partial_t w(1,t) + k_1 d \dot \theta(t))f(1), \label{CT_18}\\
\int_0^1 \frac{1}{\alpha}~\partial^2_t \phi(\cdot,t) g \ dx  &= -\int_0^1\dfrac{1}{\beta} \partial_x \phi(\cdot,t)g' \ dx - c_2 \int_0^1 \partial_t \partial_x \phi(\cdot,t)g' \ dx + \int_0^1 V(\cdot,t)g \ dx \nonumber \\
 &  +\gamma \big(\theta(t) - \phi(1,t)\big)g(1) - \mu \phi(0,t)g(0), \label{CT_19}\\
\int_0^1 V(\cdot,t)h \ dx &= \int_0^1 \partial_x w(\cdot,t)h \ dx - \int_0^1 \phi(\cdot,t)h \ dx,  \label{CT_20}
\end{align}
with the interface equation,
\begin{align}
(J+ md^2) \ddot \theta(t)+ (k_1d^2 + d k_2) \dot \theta(t)  + dm \partial_t^2 w(1,t)
  + dk_1 \partial_t w(1,t) \nonumber\\
  =  -\gamma \big(\theta(t) - \phi(1,t)\big),  \label{CT_21}
\end{align}

@@

\subsection{Galerkin approximation}
Create a set of n+1 linear basis functions $\delta_i$, where $\delta_i \in C[0,1]$ for $i = 0,1,2,...,n$. Let $S_0 = \textrm{span}\left\{\delta_0,\delta_1,\delta_2,...,\delta_n\right\}$ and $S = \textrm{span}\left\{\delta_1,\delta_2,\delta_3,...,\delta_n\right\}$. \label{sym:span}

\subsubsection{Problem G}
Find the functions $w^h$, $\phi^h$, $V^h$ and $\theta^h$ such that $w^h(\cdot,t) \in S$,  $\phi^h(\cdot,t),V^h(\cdot,t) \in S_0$ and $\theta^h(t) \in R$ for all $t>0$ and the following equations hold:

@@

\subsubsection{Problem ODE}
Find the functions $\bar{w} \in S$, $\bar{\phi}, \bar{V} \in S_0$ and $\theta^h \in R$ such that
\begin{align}
M_w\ddot{\bar{w}} = L_w\bar{V} -\big(m \ddot{w}_{n+1}(t) + k_1 \dot{w}_{n+1}(t) \big)\delta_i(1) + M^* \bar{q}(t) + \bar{q}_I,\\
\label{sys2}
\frac{1}{\alpha} M \ddot{\bar{\phi}} = -\frac{1}{\beta} K\bar{\phi} + M\bar{V} + \tilde{G},\\
\label{sys2.1}
\bar{0} = -M\bar{V} + L^T\bar{w} - M\bar{V}.
\end{align}

### 2023-11-12 files/Chapter5/2D_FEM.tex
table of symbols

\subsubsection{Reference configuration for rectangular cross-section}\label{sssec:2D_Model:RefConf}
Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$. Denote the elastic body by $\Omega \in R_2$, with $(0,0)$ as the point of reference. For a rectangular cross-section, the body $\Omega$ can be described as,
\begin{eqnarray*}
	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows:

>>>>

\subsubsection{Reference configuration for rectangular cross-section}\label{sssec:2D_Model:RefConf}
Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$. Denote the elastic body by $\Omega \in R^2$, with $(0,0)$ as the point of reference. For a rectangular cross-section, the body $\Omega$ can be described as,
\begin{eqnarray*}
	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows: \label{sym:En}
